\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-09-27 manuscript.tex
Correct some more small typos

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.57e-3} & \num{6.17e-5} & \num{-2.50e-5} \\
	\num{6.17e-5} & \num{5.57e-3} & \num{1.00e-5} \\
	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
	\end{bmatrix} \si{\kilo\gram\meter\squared} .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} [0.9,1.1,1.0], \quad k_R = 0.4 , \quad	k_\Omega = 0.296 ,\\
	c = 1.0 , \quad k_\Delta = 0.5 , \quad \alpha = 15 .
\end{gather*}
A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
\begin{table}[H]
\caption{Constraint Parameters~\label{tab:constraints}}
\begin{center}\begin{tabular}{lc}
Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline 
\([0.174,\,-0.934,\, -0.034]^T\) & \ang{40} \\ \hline 
\([0 ,\, 0.7071 ,\, 0.7071]^T\) & \ang{40} \\ \hline 
\([-0.853 ,\, 0.436 ,\, -0.286]^T\) & \ang{40} \\ \hline 
\([-0.122 ,\,-0.140,\, -0.983]^T\) & \ang{20}\end{tabular} 
\end{center}
\end{table}

@@

To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\).
As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
\begin{align*}
  A(R) \geq A(R_d) \, \forall R \in U .
\end{align*}
Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \) the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).

The desired equilibrium is occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.

>>>>

\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
  \hspace{-5mm}
	J = \begin{bmatrix}
	\num{5.57e-3} & \num{6.17e-5} & \num{-2.50e-5} \\
	\num{6.17e-5} & \num{5.57e-3} & \num{1.00e-5} \\
	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
	\end{bmatrix} \si{\kilo\gram\meter\squared} .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} [0.9,1.1,1.0], \quad k_R = 0.4 , \quad	k_\Omega = 0.296 ,\\
	c = 1.0 , \quad k_\Delta = 0.5 , \quad \alpha = 15 .
\end{gather*}
A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
\begin{table}[H]
\caption{Constraint Parameters~\label{tab:constraints}}
\begin{center}\begin{tabular}{lc}
Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline 
\([0.174,\,-0.934,\, -0.034]^T\) & \ang{40} \\ \hline 
\([0 ,\, 0.7071 ,\, 0.7071]^T\) & \ang{40} \\ \hline 
\([-0.853 ,\, 0.436 ,\, -0.286]^T\) & \ang{40} \\ \hline 
\([-0.122 ,\,-0.140,\, -0.983]^T\) & \ang{20}\end{tabular} 
\end{center}
\end{table}

@@

To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
\begin{align*}
  A(R) \geq A(R_d) \; \forall \; R \in U .
\end{align*}
Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
The desired equilibrium occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
